---
title: "EPPS 6356 Assignment 9"
format:
  html:
    code-fold: true
---

```{r include=FALSE, echo = F, warning = F}
library(ggplot2)
library(quantmod)
##library(TSstudio)
##library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

### 1. BBBYQ

The stock value of the dying memestock, GME, from its massive rise to its slow downward trajectory. This xts object goes from January 1st 2020, to June 30th, 2023

```{r, echo = F, warning = F}
### Time series of the BBBYQ memestock

getSymbols(
    Symbols = "GME"
)

GME = GME["2020-01/2023-06"]


plot(
  GME$GME.Close
)


```

### 2. Variables

The xts object has is indexed by time, with each observation being one sequential day. Each observation has the stock ticker open, high, low, and close value.

```{r, warning= F}
class(GME)
summary(GME)
```

### 3. Analysis

We will be using the close value series for the following analysis. Time span is still January 2020 to July 2023.

#### Trend analysis

Value and smoothed

```{r, echo = F}

GME = GME$GME.Close

plot(GME,
     lwd = 0.5,
     main = "Close value and month-smoothed value"
     )
lines( rollmean(GME, 14, align = "center"),
       col = "red"
       )


```

```{r, echo = F, warning= F}

### Plots from the TSstudio package

##ts_seasonal(BBBYQ, type = "")

##ts_cor(USgas)

##ts_lags(USgas, margin = .01)

```

#### Stationarity analysis

```{r}

plot(diff(GME),
     lwd = 0.5,
     main = "First differences, i.e. daily gain, and month-smoothed value"
    )
lines(diff(rollmean(GME, 14, align = "center") ),
        col = "red"
    )

```

#### pdq & PDQ

There may also be some seasonality to the data

```{r, echo = F}



acf(GME,
    main = "GME acf")
pacf(GME,
     main = "GME pacf")

GME2 = arima(GME, order = c(1,1,1) )

acf(GME2$residuals,
    main = "GME ARIMA(1,1,1)  residuals acf")
pacf(GME2$residuals,
     main = "GME ARIMA(1,1,1) residuals pacf")

plot(GME2$residuals,
     main = "GME ARIMA(1,1,1) residuals")


```
